---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(statsr)
library(readr)
library(lmtest)
library(corrplot)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
#load("movies.Rdata")
load("D:/Coursera 3 lab/movies.Rdata")




```


* * *

## Part 1: Data
The data set is comprised of 651 randomly sampled movies.

* * *

## Part 2: Research question
In this project, my boss was interested in learning what attributes make a movie popular. I chose the Rating on IMDB as the independent variable, and try to find predictors for it.

* * *

## Part 3: Exploratory data analysis
```{r, warning=FALSE}
head(movies)
str(movies)#Check the structure of the data set. This data set has 651 observations and 32 variables

summary(movies)#show summary statistics of every variable

hist(movies$imdb_rating)#The independent variable "imdb_rating" is obviously left-skewed.

#check the variables that are possibly related to the independent variable

#genre of movie
ggplot(movies, aes(x = genre, y = imdb_rating)) +
  geom_boxplot()+
  theme(axis.text.x = element_text(size=6))
#there are different pattern of rating among different genres
  
ggplot(movies, aes(x = critics_score, y = imdb_rating)) +
  geom_point()+
  geom_smooth()+
  facet_wrap(~critics_rating)
#critics score on Rotten Tomatoes and Rating on IMDB look highly correlated

ggplot(movies, aes(x = critics_score, y = audience_score))+
  geom_point()+
  geom_smooth()
#It can be seen here that audience_score and critics_score are strongly correlated, so we use only one of them in our model to avoid multicollinearity.

ggplot(movies, aes(x = mpaa_rating, y = imdb_rating))+
  geom_boxplot()
#there is not any obvious correlation between MPAA rating and imdb_rating

```

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 4: Modeling

### Model training
```{r}
newdata <- movies[,-c(1, 2, 6, 25, 26, 27, 28, 29, 30, 31, 32)]#I deleted the variables that have noting to do with the IMDB rating

lm1 <- lm(imdb_rating~., data = newdata)#the whole modle with every possible variable
summary(lm1)

#a simpler model with only significant variables shown in lm1
lm2 <- lm(imdb_rating~genre+runtime+imdb_num_votes+audience_rating:audience_score+best_pic_nom+best_actor_win+best_actress_win, data = newdata)
summary(lm2)
```
Lm2 model suggests that:
1) The variables `genre`, `runtime`, `imdb_num_votes`, audience_score` are significant predictors for the imdb rating.
2) In terms of genre, documentary, drama, mystery and suspense tend to be rated higher than others.
3) The number of votes on imdb, audience rating on Rotten Tomatoes and the runtime of movies are positively corelated to the rating.

### Model diagnostics
For the model to provide valid results, there are certain conditions that need to be met. These are:

1) Linear relationships between (numerical) x and y
2) Nearly normal residuals with mean 0
3) Constant variability of residuals
4) Independent residuals 

```{r}
plot(lm2)
```

The residuals vs fitted plot shows the mean of the residuals can be seen to equal zero. The Q-Q plot also indicates an almost normal distribution, with some deviation from normality occurring on the left-hand side, indicating again that the data is left-skewed. 

It is quite clear from the scale-position plot that the variability of residuals is not constant. The implications of this are that the values for the standard error are not entirely accurate and could therefore affect the accuracy of confidence intervals and the outcome of hypothesis tests from the model. If the model was altered to take into account the non-constancy that is present, then this would resolve this issue, however, this is outwith the scope of this project. 

* * *

## Part 5: Prediction

```{r}
Fantastic_Beasts<- data.frame(genre="Science Fiction & Fantasy", runtime = 132, imdb_num_votes =433750, audience_rating="Upright", audience_score=79, best_pic_nom = "no",best_actor_win = 'yes', best_actress_win='no')

predict(lm2, Fantastic_Beasts, intervel = "prediction", level = 0.95)
```


* * *

## Part 6: Conclusion

Because the IMDB rating of Fantastic Beasts and Where to Find Them is 7.3, the prediction in this case can be considered as correct.Future research, and improvements to the model, could stem from learning how to transform the data appropriately so that the non-constancy of the data is negated in the model. 